---
title: "STAA 566 HW2 Dynamic Graph"
author: "Sherry Schulz"
date: "2/17/2022"
output: html_document
knit: (function(input_file, encoding){out_dir<-'docs';rmarkdown::render(input_file,encoding=encoding,output_file=file.path(dirname(input_file),out_dir, 'index.html'))})
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE)
```

After quarantine and restrictions were implemented due to Covid Pandemic, many lost their jobs and businesses. I want to compare the USA and Colorado unemployment rates from 2001 to 2021. The data set is extracted from the Bureau of Labor Statistics.
For CO Unemployment Rate: https://beta.bls.gov/dataViewer/view/timeseries/LASST080000000000003
For USA Unemployment Rate:https://beta.bls.gov/dataViewer/view/timeseries/LNU04000000
I will create a comparative dynamic graphs that describe the progression of unemployment rate from 2001-2021. One can see that there is a sharp increase when pandemic initially hit. It has recovered to the previous level since then. Also, Colorado seems to follow similar trend as the overall USA trend.

```{r}
Bothdata<- read.csv("Umemployment Rate Both 2001-2021.csv")
Bothdata$DateR <- as.Date(paste(Bothdata$Date,"-01",sep=""))
```

```{r}
#install.packages("plotly")
library(plotly)
```

```{r}
plot<-plot_ly(Bothdata,
              x=~DateR,
              y=~Value,
              color= ~ID,
              colors = c("blue", "orange"),
              type="scatter",
              mode="lines"
              )
plot<-plot %>% rangeslider() %>%
  layout(title="Unemployment Rate in USA and CO from 2001-2021", xaxis=list(title="Date"), yaxis=list(title="Unemployment Rate in %"))
plot<-plot%>% layout(hovermod = "x")
plot
```



